---
title: "Clean and Merge Markit, FISD and TRACE"
date: "July 11, 2017"
output:
  html_document:
    css: bodycss.css
    fig_width: 8
    font-family: Helvetica,Arial,sans-serif;
    number_section: yes
    toc: yes
  pdf_document:
    toc: yes
  word_document:
    toc: yes
linestretch: 2
bibliography: C:\Users\dnratnadiwakara\OneDrive\library.bib
---

<style type="text/css">
body{ 
      font-size: 15px;
      font-family: Helvetica,Arial,sans-serif;
      line-height: 200%;
  }
  
.author {
 font-size: 15px;
 color: Black;
 font-style: normal;
 text-align: center;
}


.date { 
 font-size: 15px;
 color: Black;
 font-style: normal;
 text-align: center;
}

.title{
  text-align: center;
  font-size: 15px;
 color: Black;
 
}

.toc-ignore{
  text-align: center;
  font-size: 15px;
 color: Black;
}

.fluid-row{
  text-align: center;
  font-size: 15px;
 color: Black;
}

</style>

```{r setup, include=FALSE}
knitr::opts_chunk$set(warning=FALSE, message=FALSE,echo = FALSE, fig.align='center')
```



```{r initialize,message=FALSE,warning=FALSE}
rm(list=ls())
path = "E:/shortselling"
setwd(path)
require(gdata)
require(dplyr)
require(zoo)
require(plyr)
require(sqldf)
require(stargazer)
require(data.table)
require(lubridate)
require(lfe)
library(np)
library(ggplot2)

output.type="text"

ssf_data <- readRDS(file="E:/shortselling/Data/Processed/Monthly_sample_Aug172017.rds")
ssf_data['data_date'] <- as.Date(ssf_data$data_month)
ssf_data['min_option_date'] <- as.Date(ssf_data$min_option_date)

# save(t,file="SECIDs_withshortfees.rda")
```

# Descriptives
```{r descs}

stargazer(ssf_data[, c("IndicativeFee","UtilisationByQuantity","DCBS","LenderQuantityOnLoan","LendableQuantity")], type = output.type, summary.stat = c("mean", "sd", "p25", "median", "p75", "n"),notes = "",digits = 4)
```

```{r diff_in_diff}

temp <- ssf_data[(ssf_data$data_date<= ssf_data$min_option_date+90 & ssf_data$data_date>= ssf_data$min_option_date+0) | (ssf_data$data_date>= ssf_data$min_option_date-90 & ssf_data$data_date<= ssf_data$min_option_date-0),]
temp['option'] <- ifelse(temp$data_date>= temp$min_option_date,1,0)
temp <- temp[!is.na(temp$data_month),]
option_secids <- unique(temp[temp$option==1,]$SECID)
nooption_secids <- unique(temp[temp$option==0,]$SECID)
secids <- intersect(option_secids,nooption_secids)
temp <- temp[temp$SECID %in% secids,]
regs <- list()
regs[[1]] <- felm(as.formula("IndicativeFee~option|0|0|CUSIP"),data=temp)
regs[[2]] <- felm(as.formula("IndicativeFee~option+log(q_assets)+UtilisationByQuantity+AverageTenure+equity_ret_variance+m_equityreturn|0|0|CUSIP"),data=temp)

stargazer(regs,type = output.type,no.space = TRUE,dep.var.caption = "Dependent Var: Indicative Fee",dep.var.labels = c("",""))
```



```{r option}

temp <- ssf_data[ssf_data$IndicativeFee>=0.12,]
temp <- temp[is.na(temp$min_option_date) | temp$data_date>= temp$min_option_date, ]
temp['option'] <- ifelse(temp$data_date< temp$min_option_date | is.na(temp$min_option_date),0,1)
temp <- temp[!is.na(temp$data_month),]
temp <- temp[is.finite(log(temp$q_assets)),]

regs <- list()
regs[[1]] <- felm(as.formula("IndicativeFee~option|data_month|0|CUSIP"),data=temp)
regs[[2]] <- felm(as.formula("IndicativeFee~option+log(q_assets)+UtilisationByQuantity+AverageTenure+equity_ret_variance+m_equityreturn|data_month|0|CUSIP"),data=temp)

stargazer(regs,type = output.type,no.space = TRUE,dep.var.caption = "Dependent Var: Indicative Fee",dep.var.labels = c("",""))
```




```{r put_premium}

temp <- ssf_data
temp <- temp[is.na(temp$min_option_date) | temp$data_date>= temp$min_option_date, ]
temp['option'] <- ifelse(temp$data_date< temp$min_option_date | is.na(temp$min_option_date),0,1)
temp <- temp[!is.na(temp$data_month),]
temp <- temp[is.finite(log(temp$put_impl_premium)),]

regs <- list()
regs[[1]] <- felm(as.formula("IndicativeFee~log(put_impl_premium)|data_month|0|CUSIP"),data=temp)
regs[[2]] <- felm(as.formula("IndicativeFee~log(put_impl_premium)+log(q_assets)+UtilisationByQuantity+AverageTenure+equity_ret_variance+m_equityreturn|data_month|0|CUSIP"),data=temp)
regs[[3]] <- felm(as.formula("IndicativeFee~log(put_impl_premium)|data_month|0|CUSIP"),data=temp[temp$IndicativeFee>=quantile(temp$IndicativeFee,0.95),])
regs[[4]] <- felm(as.formula("IndicativeFee~log(put_impl_premium)+log(q_assets)+UtilisationByQuantity+AverageTenure+equity_ret_variance+m_equityreturn|data_month|0|CUSIP"),data=temp[temp$IndicativeFee>=quantile(temp$IndicativeFee,0.95),])


stargazer(regs,type = output.type,no.space = TRUE,dep.var.caption = "Dependent Var: Indicative Fee",dep.var.labels = c("All","All","Fee > p95","Fee > p95"))
```
```{r prem_kernal_reg}

# temp <- ssf_data[ssf_data$IndicativeFee<=quantile(ssf_data$IndicativeFee,0.99),]
# 
# temp <- temp[!is.na(temp$data_month),]
# temp <- temp[is.finite(log(temp$put_impl_premium)),]
# 
# put_impl_premium <- felm(put_impl_premium~0|factor(data_month),data=temp)
# temp['resid_put_impl_premium'] <- put_impl_premium$residuals
# 
# IndicativeFee <- felm(IndicativeFee~0|factor(data_month),data=temp)
# temp['resid_IndicativeFee'] <- IndicativeFee$residuals
# 
# temp <- temp[temp$resid_put_impl_premium <= quantile(temp$resid_put_impl_premium,0.99),]
# temp <- temp[temp$resid_put_impl_premium <= quantile(temp$resid_IndicativeFee,0.99),]
# 
# bw <- npregbw(formula=as.vector(temp$resid_put_impl_premium)~as.vector(temp$resid_IndicativeFee),bws=(max(temp$IndicativeFee)-min(temp$IndicativeFee))/5,bwtype="fixed",bandwidth.compute=F)
# 
# model <- npreg(bws=bw,gradients = TRUE)
# plot.out <- plot(model, plot.errors.method="asymptotic",plot.errors.style="band",plot.behavior="data")
# y.eval <- fitted(plot.out$r1)
# x.eval <- plot.out$r1$eval[,1]#/10000+mean(loan_data[loan_data$ne_cutoff==-0.3,]$mpay_value,na.rm=TRUE)
# y.se <- se(plot.out$r1)
# y.lower.ci <- y.eval+y.se[,1]*1.96
# y.upper.ci <- y.eval+y.se[,2]*1.96
# df <- as.data.frame(cbind(x.eval,y.eval,y.lower.ci,y.upper.ci))
# 
# 
# df <- melt(df,id="x.eval")
# saveRDS(df,file="E:/shortselling/Data/Processed/put_prem_fee_kr.rds")

df = readRDS(file="E:/shortselling/Data/Processed/put_prem_fee_kr.rds")
g1 <-  ggplot(df,aes(x=x.eval, y=value,colour=variable)) + geom_line(aes(linetype=variable), size=1) +scale_linetype_manual(values = c(1,2,2))+scale_colour_manual(values=c("black","gray40","gray40"))+ theme_bw()+ylab("Put Premium") + xlab("Indicative Fee")+ labs(title = "")+ theme(legend.position="none")#+scale_y_continuous(limits = c(0.05, 0.06))
g1
```


```{r put_premium_double_sort}
temp <- ssf_data[is.finite(log(ssf_data$put_impl_premium)),]
months <- unique(ssf_data$data_month)

sorted_data <- NULL
for(month in months) {
  tryCatch({
    t <- temp[temp$data_month==month,]
    # t['fee_quintile'] <- ntile(t$IndicativeFee,5)
    # t <- t[t$fee_quintile==5,]
    #  t['fee_quintile'] <- ntile(t$IndicativeFee,5)
    #  t <- t[t$fee_quintile==5,]
     t['fee_quintile'] <- ntile(t$IndicativeFee,100)
    t['premium_quintile'] <- 1#ntile(t$put_impl_premium,5)
    t['fee_percentile'] <- t$fee_quintile#paste("Fee",t$fee_quintile,", Prem",t$premium_quintile)
    t <- ddply(t,.(fee_percentile),summarise,fee=mean(IndicativeFee),prem=mean(put_impl_premium))
    sorted_data <- rbind(sorted_data,t)
  },error=function(e){})
}

sorted_data <- ddply(sorted_data,.(fee_percentile),summarise,fee=mean(fee),prem=mean(prem))
sorted_data$fee <- sorted_data$fee*4

sorted_data <- melt(sorted_data,id="fee_percentile")

g2 <-  ggplot(sorted_data,aes(x=fee_percentile, y=value,colour=variable)) + geom_line(aes(linetype=variable), size=1) +scale_linetype_manual(values = c(1,2))+scale_colour_manual(values=c("black","gray40"))+ theme_bw()+ylab("Put Premium") + xlab(" Fee Percentile")+ labs(title = "")+ theme(legend.position="bottom")#+scale_y_continuous(limits = c(0.05, 0.06))
g2
```


```{r call_premium_double_sort}
temp <- ssf_data[is.finite(log(ssf_data$put_impl_premium)),]
months <- unique(ssf_data$data_month)
temp['lendable_frac'] <- temp$LendableQuantity/(temp$sharesoutstanding*1e6)
temp['on_loan_frac'] <- temp$LenderQuantityOnLoan/temp$LendableQuantity
temp['put_vol_open_int'] <- temp$put_opt_volume/temp$put_opt_open_interest
temp['call_vol_open_int'] <- temp$call_opt_volume/temp$call_opt_open_interest

temp$put_vol_open_int <- ifelse(!is.finite(temp$put_vol_open_int),NA,temp$put_vol_open_int)
temp$call_vol_open_int <- ifelse(!is.finite(temp$call_vol_open_int),NA,temp$call_vol_open_int)

sorted_data <- NULL
for(month in months) {
  tryCatch({
    t <- temp[temp$data_month==month,]
    # t['fee_quintile'] <- ntile(t$IndicativeFee,5)
    # t <- t[t$fee_quintile==5,]
    #  t['fee_quintile'] <- ntile(t$IndicativeFee,5)
    #  t <- t[t$fee_quintile==5,]
     t['fee_quintile'] <- ntile(t$IndicativeFee,20)
    t['premium_quintile'] <- 1#ntile(t$put_impl_premium,5)
    t['fee_percentile'] <- t$fee_quintile#paste("Fee",t$fee_quintile,", Prem",t$premium_quintile)
    t <- ddply(t,.(fee_percentile),summarise,fee=mean(IndicativeFee),call_prem=mean(call_impl_premium,na.rm=TRUE),put_prem=mean(put_impl_premium),call_volatility = mean(call_impl_volatility,na.rm=TRUE),put_volatility = mean(put_impl_volatility,na.rm=TRUE),equity_ret_variance=mean(equity_ret_variance,na.rm=TRUE),m_equityreturn=mean(m_equityreturn,na.rm=TRUE),lendable_frac = mean(lendable_frac,na.rm=TRUE),on_loan_frac=mean(on_loan_frac,na.rm=TRUE),put_vol_open_int=mean(put_vol_open_int,na.rm=TRUE),call_vol_open_int=mean(call_vol_open_int,na.rm=TRUE))
    sorted_data <- rbind(sorted_data,t)
  },error=function(e){})
}

sorted_data <- ddply(sorted_data,.(fee_percentile),summarise,fee=mean(fee),call_prem=mean(call_prem),put_prem=mean(put_prem),call_volatility = mean(call_volatility),put_volatility =mean(put_volatility), equity_ret_variance=mean(equity_ret_variance), m_equityreturn=mean(m_equityreturn),lendable_frac = mean(lendable_frac),on_loan_frac=mean(on_loan_frac), put_vol_open_int = mean(put_vol_open_int), call_vol_open_int = mean(call_vol_open_int))

sd = sorted_data

sorted_data$fee <- sorted_data$fee*4
sorted_data$call_volatility <- sorted_data$call_volatility*2
sorted_data$put_volatility <- sorted_data$put_volatility*2
sorted_data$m_equityreturn <- NULL#sorted_data$m_equityreturn*100
sorted_data$equity_ret_variance <- sorted_data$equity_ret_variance*1000
# sorted_data$call_prem <- NULL
# sorted_data$put_prem <- NULL
sorted_data$on_loan_frac <- NULL
sorted_data$lendable_frac <- NULL
sorted_data$call_vol_open_int <- sorted_data$call_vol_open_int/4 
sorted_data$put_vol_open_int <- sorted_data$put_vol_open_int/4

sorted_data <- melt(sorted_data,id="fee_percentile")


g2 <-  ggplot(sorted_data,aes(x=fee_percentile, y=value,colour=variable)) + geom_line(aes(linetype=variable), size=1) +scale_linetype_manual(values = c(1,1,1,1,1,1,1,1))+scale_colour_manual(values=c("black","blue","red","green","darkgreen","purple","coral3","goldenrod"))+ theme_bw()+ylab("") + xlab(" Fee Percentile")+ labs(title = "")+ theme(legend.position="bottom")+  ylim(0,2.5)+theme(axis.text.y=element_blank())#+scale_y_continuous(limits = c(0.05, 0.06))
g2
```

