---
title: "Title"
date: "November 12, 2017"
output:
  html_document:
    css: bodycss.css
    fig_width: 8
    font-family: Helvetica,Arial,sans-serif;
    number_section: yes
    toc: yes
  pdf_document:
    toc: yes
  word_document:
    toc: yes
linestretch: 2
bibliography: C:\Users\dnratnadiwakara\OneDrive\library.bib
---

<style type="text/css">
body{ 
      font-size: 15px;
      font-family: Helvetica,Arial,sans-serif;
      line-height: 200%;
  }
  
.author {
 font-size: 15px;
 color: Black;
 font-style: normal;
 text-align: center;
}


.date { 
 font-size: 15px;
 color: Black;
 font-style: normal;
 text-align: center;
}

.title{
  text-align: center;
  font-size: 15px;
 color: Black;
 
}

.toc-ignore{
  text-align: center;
  font-size: 15px;
 color: Black;
}

.fluid-row{
  text-align: center;
  font-size: 15px;
 color: Black;
}

</style>

```{r setup, include=FALSE}
knitr::opts_chunk$set(warning=FALSE, message=FALSE,echo = FALSE, fig.align='center')
```



```{r initialize,message=FALSE,warning=FALSE}
rm(list=ls())
path = "E:/shortselling"
setwd(path)
require(gdata)
require(dplyr)
require(zoo)
require(plyr)
require(sqldf)
require(stargazer)
require(data.table)
require(lubridate)
require(lfe)
library(np)
library(ggplot2)

output.type="text"

ssf_data <- readRDS(file="E:/shortselling/Data/Processed/Monthly_sample_Nov122017.rds")
ssf_data <- as.data.frame(ssf_data)
ssf_data['data_date'] <- as.Date(ssf_data$data_month)

```

# Descriptives
```{r descs}

stargazer(ssf_data[, c("IndicativeFee","UtilisationByQuantity","DCBS","LenderQuantityOnLoan","LendableQuantity")], type = output.type, summary.stat = c("mean", "sd", "p25", "median", "p75", "n"),notes = "",digits = 4)
```



```{r put_premium_double_sort}
temp <- ssf_data[is.finite(log(ssf_data$put_bid_ask)),]
months <- unique(ssf_data$data_month)
library(psych)
trim = 0.005

sorted_data <- NULL
for(month in months) {
  tryCatch({
    t <- temp[temp$data_month==month,]
    # t['fee_quintile'] <- ntile(t$IndicativeFee,5)
    # t <- t[t$fee_quintile==5,]
    #  t['fee_quintile'] <- ntile(t$IndicativeFee,5)
    #  t <- t[t$fee_quintile==5,]
     t['fee_quintile'] <- ntile(t$IndicativeFee,20)
    t['premium_quintile'] <- 1#ntile(t$put_impl_premium,5)
    t['fee_percentile'] <- t$fee_quintile#paste("Fee",t$fee_quintile,", Prem",t$premium_quintile)
    t <- ddply(t,.(fee_percentile),summarise,
               fee=winsor.mean(IndicativeFee,trim = trim,na.rm=TRUE),
               call_bid_ask=winsor.mean(call_bid_ask,trim = trim,na.rm=TRUE),
               call_option_volume_at_the_money =winsor.mean(call_option_volume_at_the_money/sharesoutstanding,trim = trim,na.rm=TRUE),
               call_premium_to_strike = winsor.mean(call_premium_to_strike,trim = trim,na.rm=TRUE),
               call_open_interest_at_the_money = winsor.mean(call_open_interest_at_the_money/sharesoutstanding,trim = trim,na.rm=TRUE),
               call_impl_volatility = winsor.mean(call_impl_volatility,trim = trim,na.rm=TRUE),
               put_bid_ask=winsor.mean(put_bid_ask,trim = trim,na.rm=TRUE),
               put_option_volume_at_the_money =winsor.mean(put_option_volume_at_the_money/sharesoutstanding,trim = trim,na.rm=TRUE),
               put_premium_to_strike = winsor.mean(put_premium_to_strike,trim = trim,na.rm=TRUE),
               put_open_interest_at_the_money = winsor.mean(put_open_interest_at_the_money/sharesoutstanding,trim = trim,na.rm=TRUE),
               put_impl_volatility = winsor.mean(put_impl_volatility,trim = trim,na.rm=TRUE),
               equity_volume_to_outstanding = winsor.mean(m_sharevolume/sharesoutstanding,trim = trim,na.rm=TRUE),
               market_to_book = winsor.mean(market_value/q_equity,trim = trim,na.rm=TRUE),
               m_equityreturn = winsor.mean(m_equityreturn,trim = trim,na.rm=TRUE),
               equity_ret_variance = winsor.mean(equity_ret_variance,trim = trim,na.rm=TRUE),
               UtilisationByQuantity = winsor.mean(UtilisationByQuantity,trim = trim,na.rm=TRUE),
               no_of_companies = length(unique(SECID))
             )
    t['month'] = month
    sorted_data <- rbind(sorted_data,t)
  },error=function(e){})
}

monthly_data <- sorted_data
monthly_data['year'] <- floor(monthly_data$month)
sorted_data <- ddply(monthly_data,.(fee_percentile),summarise,
                     fee=winsor.mean(fee,trim = trim,na.rm = TRUE),
                     call_bid_ask=winsor.mean(call_bid_ask,trim = trim,na.rm=TRUE),
                     call_option_volume_at_the_money =winsor.mean(call_option_volume_at_the_money,trim = trim,na.rm=TRUE),
                     call_premium_to_strike = winsor.mean(call_premium_to_strike,trim = trim,na.rm=TRUE),
                     call_open_interest_at_the_money = winsor.mean(call_open_interest_at_the_money,trim = trim,na.rm=TRUE),
                     call_impl_volatility = winsor.mean(call_impl_volatility,trim = trim,na.rm=TRUE),
                     put_bid_ask=winsor.mean(put_bid_ask,trim = trim,na.rm=TRUE),
                     put_option_volume_at_the_money =winsor.mean(put_option_volume_at_the_money,trim = trim,na.rm=TRUE),
                     put_premium_to_strike = winsor.mean(put_premium_to_strike,trim = trim,na.rm=TRUE),
                     put_open_interest_at_the_money = winsor.mean(put_open_interest_at_the_money,trim = trim,na.rm=TRUE),
                     put_impl_volatility = winsor.mean(put_impl_volatility,trim = trim,na.rm=TRUE),
                     equity_volume_to_outstanding = winsor.mean(equity_volume_to_outstanding,trim = trim,na.rm=TRUE),
                     market_to_book = winsor.mean(market_to_book,trim = trim,na.rm=TRUE),
                     m_equityreturn = winsor.mean(m_equityreturn,trim = trim,na.rm=TRUE),
                     equity_ret_variance = winsor.mean(equity_ret_variance,trim = trim,na.rm=TRUE),
                     UtilisationByQuantity = winsor.mean(UtilisationByQuantity,trim = trim,na.rm=TRUE),
                     no_of_companies = median(no_of_companies,na.rm=TRUE)
               )

sorted_data_yearly <- ddply(monthly_data,.(fee_percentile,year),summarise,
                     fee=winsor.mean(fee,trim = trim,na.rm = TRUE),
                     call_bid_ask=winsor.mean(call_bid_ask,trim = trim,na.rm=TRUE),
                     call_option_volume_at_the_money =winsor.mean(call_option_volume_at_the_money,trim = trim,na.rm=TRUE),
                     call_premium_to_strike = winsor.mean(call_premium_to_strike,trim = trim,na.rm=TRUE),
                     call_open_interest_at_the_money = winsor.mean(call_open_interest_at_the_money,trim = trim,na.rm=TRUE),
                     call_impl_volatility = winsor.mean(call_impl_volatility,trim = trim,na.rm=TRUE),
                     put_bid_ask=winsor.mean(put_bid_ask,trim = trim,na.rm=TRUE),
                     put_option_volume_at_the_money =winsor.mean(put_option_volume_at_the_money,trim = trim,na.rm=TRUE),
                     put_premium_to_strike = winsor.mean(put_premium_to_strike,trim = trim,na.rm=TRUE),
                     put_open_interest_at_the_money = winsor.mean(put_open_interest_at_the_money,trim = trim,na.rm=TRUE),
                     put_impl_volatility = winsor.mean(put_impl_volatility,trim = trim,na.rm=TRUE),
                     equity_volume_to_outstanding = winsor.mean(equity_volume_to_outstanding,trim = trim,na.rm=TRUE),
                     market_to_book = winsor.mean(market_to_book,trim = trim,na.rm=TRUE),
                     m_equityreturn = winsor.mean(m_equityreturn,trim = trim,na.rm=TRUE),
                     equity_ret_variance = winsor.mean(equity_ret_variance,trim = trim,na.rm=TRUE),
                     UtilisationByQuantity = winsor.mean(UtilisationByQuantity,trim = trim,na.rm=TRUE)
               )


# write.csv(sorted_data,file="sorted_data.csv")
```


```{r call_premium_double_sort}
temp <- ssf_data[is.finite(log(ssf_data$put_impl_premium)),]
months <- unique(ssf_data$data_month)
temp['lendable_frac'] <- temp$LendableQuantity/(temp$sharesoutstanding*1e6)
temp['on_loan_frac'] <- temp$LenderQuantityOnLoan/temp$LendableQuantity
temp['put_vol_open_int'] <- temp$put_opt_volume/temp$put_opt_open_interest
temp['call_vol_open_int'] <- temp$call_opt_volume/temp$call_opt_open_interest

temp$put_vol_open_int <- ifelse(!is.finite(temp$put_vol_open_int),NA,temp$put_vol_open_int)
temp$call_vol_open_int <- ifelse(!is.finite(temp$call_vol_open_int),NA,temp$call_vol_open_int)

sorted_data <- NULL
for(month in months) {
  tryCatch({
    t <- temp[temp$data_month==month,]
    # t['fee_quintile'] <- ntile(t$IndicativeFee,5)
    # t <- t[t$fee_quintile==5,]
    #  t['fee_quintile'] <- ntile(t$IndicativeFee,5)
    #  t <- t[t$fee_quintile==5,]
     t['fee_quintile'] <- ntile(t$IndicativeFee,20)
    t['premium_quintile'] <- 1#ntile(t$put_impl_premium,5)
    t['fee_percentile'] <- t$fee_quintile#paste("Fee",t$fee_quintile,", Prem",t$premium_quintile)
    t <- ddply(t,.(fee_percentile),summarise,fee=mean(IndicativeFee),call_prem=mean(call_impl_premium,na.rm=TRUE),put_prem=mean(put_impl_premium),call_volatility = mean(call_impl_volatility,na.rm=TRUE),put_volatility = mean(put_impl_volatility,na.rm=TRUE),equity_ret_variance=mean(equity_ret_variance,na.rm=TRUE),m_equityreturn=mean(m_equityreturn,na.rm=TRUE),lendable_frac = mean(lendable_frac,na.rm=TRUE),on_loan_frac=mean(on_loan_frac,na.rm=TRUE),put_vol_open_int=mean(put_vol_open_int,na.rm=TRUE),call_vol_open_int=mean(call_vol_open_int,na.rm=TRUE))
    sorted_data <- rbind(sorted_data,t)
  },error=function(e){})
}

sorted_data <- ddply(sorted_data,.(fee_percentile),summarise,fee=mean(fee),call_prem=mean(call_prem),put_prem=mean(put_prem),call_volatility = mean(call_volatility),put_volatility =mean(put_volatility), equity_ret_variance=mean(equity_ret_variance), m_equityreturn=mean(m_equityreturn),lendable_frac = mean(lendable_frac),on_loan_frac=mean(on_loan_frac), put_vol_open_int = mean(put_vol_open_int), call_vol_open_int = mean(call_vol_open_int))

sd = sorted_data

sorted_data$fee <- sorted_data$fee*4
sorted_data$call_volatility <- sorted_data$call_volatility*2
sorted_data$put_volatility <- sorted_data$put_volatility*2
sorted_data$m_equityreturn <- NULL#sorted_data$m_equityreturn*100
sorted_data$equity_ret_variance <- sorted_data$equity_ret_variance*1000
# sorted_data$call_prem <- NULL
# sorted_data$put_prem <- NULL
sorted_data$on_loan_frac <- NULL
sorted_data$lendable_frac <- NULL
sorted_data$call_vol_open_int <- sorted_data$call_vol_open_int/4 
sorted_data$put_vol_open_int <- sorted_data$put_vol_open_int/4

sorted_data <- melt(sorted_data,id="fee_percentile")


g2 <-  ggplot(sorted_data,aes(x=fee_percentile, y=value,colour=variable)) + geom_line(aes(linetype=variable), size=1) +scale_linetype_manual(values = c(1,1,1,1,1,1,1,1))+scale_colour_manual(values=c("black","blue","red","green","darkgreen","purple","coral3","goldenrod"))+ theme_bw()+ylab("") + xlab(" Fee Percentile")+ labs(title = "")+ theme(legend.position="bottom")+  ylim(0,2.5)+theme(axis.text.y=element_blank())#+scale_y_continuous(limits = c(0.05, 0.06))
g2
```

