---
title: "Title"
date: "November 12, 2017"
output:
  html_document:
    css: bodycss.css
    fig_width: 8
    font-family: Helvetica,Arial,sans-serif;
    number_section: yes
    toc: yes
  pdf_document:
    toc: yes
  word_document:
    toc: yes
linestretch: 2
bibliography: C:\Users\dnratnadiwakara\OneDrive\library.bib
---

<style type="text/css">
body{ 
      font-size: 15px;
      font-family: Helvetica,Arial,sans-serif;
      line-height: 200%;
  }
  
.author {
 font-size: 15px;
 color: Black;
 font-style: normal;
 text-align: center;
}


.date { 
 font-size: 15px;
 color: Black;
 font-style: normal;
 text-align: center;
}

.title{
  text-align: center;
  font-size: 15px;
 color: Black;
 
}

.toc-ignore{
  text-align: center;
  font-size: 15px;
 color: Black;
}

.fluid-row{
  text-align: center;
  font-size: 15px;
 color: Black;
}

</style>

```{r setup, include=FALSE}
knitr::opts_chunk$set(warning=FALSE, message=FALSE,echo = FALSE, fig.align='center')
```



```{r initialize,message=FALSE,warning=FALSE}
rm(list=ls())
path = "E:/shortselling"
setwd(path)
require(gdata)
require(dplyr)
require(zoo)
require(plyr)
require(sqldf)
require(stargazer)
require(data.table)
require(lubridate)
require(lfe)
library(np)
library(ggplot2)

output.type="text"

ssf_data <- readRDS(file="E:/shortselling/Data/Processed/Monthly_sample_Nov122017.rds")
ssf_data <- as.data.frame(ssf_data)
ssf_data['data_date'] <- as.Date(ssf_data$data_month)

```

# Descriptives
```{r descs}

stargazer(ssf_data[, c("IndicativeFee","UtilisationByQuantity","DCBS","LenderQuantityOnLoan","LendableQuantity")], type = output.type, summary.stat = c("mean", "sd", "p25", "median", "p75", "n"),notes = "",digits = 4)
```

```{r delta_hedged_descriptives}
delta_hedged <- read.csv(file="E:/shortselling/Data/Processed/delta_hedged_returns_Nov202017.csv",sep="|",header = FALSE)
names(delta_hedged) <- c("secid","optionid","investment_date","maturity_date","strike_price","c_t","s_t","s_t_T","term1","term2","term2_alt","payoff","investment","no_of_days_traded","dh_bid_ask_t","dh_option_volume_mean","dh_open_interest_mean","last_traded_date","c_t_T","dh_impl_volatility","delta")

 # record <- c(call[1,]$secid,optionid,investment_date,maturity_date,call[nrow(call),]$strike_price,call[1,]$c_t,call[1,]$underlying_price,call[nrow(call),]$underlying_price,term1,term2,term2_alt,payoff,investment,nrow(call),call[1,]$bid_ask,mean(call$option_volume,na.rm = TRUE),mean(call$open_interest,na.rm = TRUE),call[nrow(call),]$date,call[nrow(call),]$c_t,call[1,]$impl_volatility,call[(nrow(call)-1),]$delta)
 
delta_hedged$investment_date <- as.Date(delta_hedged$investment_date)
delta_hedged$maturity_date <- as.Date(delta_hedged$maturity_date)
delta_hedged$last_traded_date <- as.Date(delta_hedged$last_traded_date)

delta_hedged['delta_hedged_return'] <- (delta_hedged$payoff - delta_hedged$term1 - delta_hedged$term2)/delta_hedged$investment
delta_hedged['time_to_maturity'] <- as.numeric(delta_hedged$maturity_date -delta_hedged$investment_date)
delta_hedged['time_to_mat_from_last_trd_date'] <- as.numeric(delta_hedged$maturity_date-delta_hedged$last_traded_date)
delta_hedged['moneyness'] <- delta_hedged$s_t/delta_hedged$strike_price

  # permcos <- unique(ssf_data$PERMCO)
  # permcos <- permcos[!is.na(permcos)]
  # permcos <- paste("",permcos,"",collapse=", ",sep="")
  # run_query(paste("select DATE,PERMCO,DIVAMT  from CRSPA.DSE where DISTCD<=1999 and DISTCD>=1000 and year(DATE)>=2002 and PERMCO in (",permcos,") and DIVAMT>0",sep=""))
  # fetch_last_query(name="dividend",rows = -1)
  # dividend$DATE <- as.Date(dividend$DATE)
  # saveRDS(dividend, file="E:/shortselling/Data/Processed/dividend.rds")

dividend <- readRDS(file="E:/shortselling/Data/Processed/dividend.rds")

temp_dh <- delta_hedged[delta_hedged$no_of_days_traded>30 & delta_hedged$time_to_mat_from_last_trd_date<=1, c("secid","investment_date","delta_hedged_return","dh_impl_volatility","c_t","strike_price","dh_bid_ask_t","maturity_date","time_to_mat_from_last_trd_date","no_of_days_traded","moneyness","time_to_maturity","s_t","c_t")]
temp_dh['data_month'] <- as.yearmon(temp_dh$investment_date)

short_fee_dh <- merge(ssf_data,temp_dh,by.x=c("SECID","data_month"),by.y=c("secid","data_month"))

short_fee_dh['month1'] <- as.yearmon(short_fee_dh$investment_date)
short_fee_dh['month2'] <- as.yearmon(short_fee_dh$investment_date+28)
short_fee_dh['month3'] <- as.yearmon(short_fee_dh$maturity_date)
dividend['month1'] <- as.yearmon(dividend$DATE)
dividend <- dividend[!duplicated(dividend[c("month1","PERMCO")]),]
short_fee_dh <- merge(short_fee_dh,dividend[,c("month1","PERMCO","DATE")],by=c("month1","PERMCO"),all.x = TRUE)
dividend$month1 <- NULL
dividend['month2'] <- as.yearmon(dividend$DATE)
short_fee_dh <- merge(short_fee_dh,dividend[,c("month2","PERMCO","DATE")],by=c("month2","PERMCO"),all.x = TRUE)
dividend['month3'] <- as.yearmon(dividend$DATE)
names(dividend) <- c( "DATE.z","PERMCO","DIVAMT","month2","month3")
dividend$month2 <- NULL
short_fee_dh <- merge(short_fee_dh,dividend[,c("month3","PERMCO","DATE.z")],by=c("month3","PERMCO"),all.x = TRUE)

short_fee_dh <- as.data.frame(short_fee_dh)
short_fee_dh['div_date'] <- short_fee_dh$DATE.y
short_fee_dh$div_date <- ifelse(is.na(short_fee_dh$div_date),short_fee_dh$DATE.z,short_fee_dh$div_date)
short_fee_dh$div_date <- ifelse(is.na(short_fee_dh$div_date),short_fee_dh$DATE.x,short_fee_dh$div_date)
short_fee_dh$DATE.x <- NULL
short_fee_dh$DATE.y <- NULL
short_fee_dh$DATE.z <- NULL

short_fee_dh <- short_fee_dh[is.na(short_fee_dh$div_date) | (short_fee_dh$div_date<= short_fee_dh$investment_date | short_fee_dh$div_date>= short_fee_dh$maturity_date),]
short_fee_dh <- short_fee_dh[short_fee_dh$s_t >= short_fee_dh$c_t,]

stargazer(short_fee_dh[short_fee_dh$no_of_days_traded>30 & short_fee_dh$time_to_mat_from_last_trd_date<=1, c("delta_hedged_return","time_to_maturity","moneyness")], type = output.type, summary.stat = c("mean", "sd", "p25", "median", "p75", "n"),notes = "",digits = 4)
```

```{r merge_delta_hedged_returns_with_shorting_fees}

# temp_dh <- delta_hedged[delta_hedged$no_of_days_traded>30 & delta_hedged$time_to_mat_from_last_trd_date<=1, c("secid","investment_date","delta_hedged_return","dh_impl_volatility","c_t","strike_price","dh_bid_ask_t")]
# temp_dh['data_month'] <- as.yearmon(temp_dh$investment_date)
# temp_dh$investment_date <- NULL
# 
# 
# short_fee_dh <- merge(ssf_data,temp_dh,by.x=c("SECID","data_month"),by.y=c("secid","data_month"))

months <- unique(short_fee_dh$data_month)
library(psych)
trim = 0.005



sorted_data <- NULL
for(month in months) {
  tryCatch({
    t <- short_fee_dh[short_fee_dh$data_month==month,]
    if(nrow(t)<20) next
    reg1 <- lm(log(IndicativeFee)~dh_impl_volatility,data=t)
    # print(summary(reg1)$adj.r.squared)
    
    t['resid_fee'] <- reg1$residuals
     t['fee_pf'] <- 1#ntile(t$resid_fee,10)
    t['vol_pf'] <- ntile(t$dh_impl_volatility,10)
   
    t['premium_to_strike']<-t$c_t/t$strike_price

    t <- ddply(t,.(fee_pf,vol_pf),summarise,
               # fee=winsor.mean(IndicativeFee,trim = trim,na.rm=TRUE),
               # equity_ret_variance = winsor.mean(equity_ret_variance,trim = trim,na.rm=TRUE),
               # dh_impl_volatility = winsor.mean(dh_impl_volatility,trim = trim,na.rm=TRUE),
               # resid_fee =  winsor.mean(resid_fee,trim = trim,na.rm=TRUE),
               # premium_to_strike = winsor.mean(premium_to_strike,trim = trim,na.rm=TRUE),
               # dh_bid_ask_t = winsor.mean(dh_bid_ask_t,trim = trim,na.rm=TRUE),
               # UtilisationByQuantity = winsor.mean(UtilisationByQuantity,trim = trim,na.rm=TRUE),
               # no_of_companies = length(unique(SECID)),
               delta_hedged_return=winsor.mean(delta_hedged_return,trim=trim,na.rm=TRUE)
             )
    t['month'] = month
    sorted_data <- rbind(sorted_data,t)
  },error=function(e){})
}



vol_sorted_data <- ddply(sorted_data,.(fee_pf,vol_pf),summarise,
                     # fee=winsor.mean(fee,trim = trim,na.rm = TRUE),
                     # equity_ret_variance = winsor.mean(equity_ret_variance,trim = trim,na.rm=TRUE),
                     # dh_impl_volatility = winsor.mean(dh_impl_volatility,trim = trim,na.rm=TRUE),
                     # resid_fee =  winsor.mean(resid_fee,trim = trim,na.rm=TRUE),
                     # premium_to_strike = winsor.mean(premium_to_strike,trim = trim,na.rm=TRUE),
                     # dh_bid_ask_t = winsor.mean(dh_bid_ask_t,trim = trim,na.rm=TRUE),
                     # # UtilisationByQuantity = winsor.mean(UtilisationByQuantity,trim = trim,na.rm=TRUE),
                     # no_of_companies = median(no_of_companies,na.rm=TRUE),
                     delta_hedged_return = winsor.mean(delta_hedged_return,trim=trim,na.rm = TRUE)
               )

g1 <- ggplot(data=vol_sorted_data, aes(x=vol_pf, y=delta_hedged_return)) +
    geom_bar(stat="identity")
g1

sorted_data <- NULL
for(month in months) {
  tryCatch({
    t <- short_fee_dh[short_fee_dh$data_month==month,]
    if(nrow(t)<20) next
    reg1 <- lm(log(IndicativeFee)~dh_impl_volatility,data=t)
    # print(summary(reg1)$adj.r.squared)
    
    t['resid_fee'] <- reg1$residuals
     t['fee_pf'] <- ntile(t$resid_fee,10)
    t['vol_pf'] <- 1#ntile(t$dh_impl_volatility,10)
   
    t['premium_to_strike']<-t$c_t/t$strike_price

    t <- ddply(t,.(fee_pf,vol_pf),summarise,
               # fee=winsor.mean(IndicativeFee,trim = trim,na.rm=TRUE),
               # equity_ret_variance = winsor.mean(equity_ret_variance,trim = trim,na.rm=TRUE),
               # dh_impl_volatility = winsor.mean(dh_impl_volatility,trim = trim,na.rm=TRUE),
               # resid_fee =  winsor.mean(resid_fee,trim = trim,na.rm=TRUE),
               # premium_to_strike = winsor.mean(premium_to_strike,trim = trim,na.rm=TRUE),
               # dh_bid_ask_t = winsor.mean(dh_bid_ask_t,trim = trim,na.rm=TRUE),
               # UtilisationByQuantity = winsor.mean(UtilisationByQuantity,trim = trim,na.rm=TRUE),
               # no_of_companies = length(unique(SECID)),
               delta_hedged_return=winsor.mean(delta_hedged_return,trim=trim,na.rm=TRUE)
             )
    t['month'] = month
    sorted_data <- rbind(sorted_data,t)
  },error=function(e){})
}





monthly_data <- sorted_data
monthly_data['year'] <- floor(monthly_data$month)
sorted_data <- ddply(monthly_data,.(fee_pf,vol_pf),summarise,
                     # fee=winsor.mean(fee,trim = trim,na.rm = TRUE),
                     # equity_ret_variance = winsor.mean(equity_ret_variance,trim = trim,na.rm=TRUE),
                     # dh_impl_volatility = winsor.mean(dh_impl_volatility,trim = trim,na.rm=TRUE),
                     # resid_fee =  winsor.mean(resid_fee,trim = trim,na.rm=TRUE),
                     # premium_to_strike = winsor.mean(premium_to_strike,trim = trim,na.rm=TRUE),
                     # dh_bid_ask_t = winsor.mean(dh_bid_ask_t,trim = trim,na.rm=TRUE),
                     # # UtilisationByQuantity = winsor.mean(UtilisationByQuantity,trim = trim,na.rm=TRUE),
                     # no_of_companies = median(no_of_companies,na.rm=TRUE),
                     delta_hedged_return = winsor.mean(delta_hedged_return,trim=trim,na.rm = TRUE)
               )
g2 <- ggplot(data=sorted_data, aes(x=fee_pf, y=delta_hedged_return)) +
    geom_bar(stat="identity")
g2

im_vol <- monthly_data[monthly_data$fee_pf %in% c(1,8,10),c("fee_pf","delta_hedged_return","month")]


months <- unique(im_vol$month)

im_vol_summary <- NULL
for(month in months) {
  temp <- im_vol[im_vol$month==month,]
  im_vol_summary <- rbind(im_vol_summary,c(month,temp[temp$fee_pf==1,]$delta_hedged_return,temp[temp$fee_pf==8,]$delta_hedged_return,temp[temp$fee_pf==10,]$delta_hedged_return))
}
im_vol_summary <- as.data.frame(im_vol_summary)
names(im_vol_summary) <- c("month","d1","d8","d10")
im_vol_summary['d8_d1'] <- im_vol_summary$d8-im_vol_summary$d1
# im_vol_summary['d10_d8'] <- im_vol_summary$d10-im_vol_summary$d8
im_vol_summary['d10_d1'] <- im_vol_summary$d10 - im_vol_summary$d1

im_vol_summary$d1 <- NULL
im_vol_summary$d8 <- NULL
im_vol_summary$d10 <- NULL

im_vol_summary <- melt(im_vol_summary,id="month")
im_vol_summary$variable <- as.character(im_vol_summary$variable)
cutoff <- data.frame( x = c(-Inf, Inf), y = 0, cutoff = factor(0) )

g3 <-  ggplot(im_vol_summary,aes(x=month, y=value,colour=variable)) + geom_line(aes(linetype=variable), size=1) +scale_linetype_manual(values = c(1,1))+scale_colour_manual(values=c("black","red"))+ theme_bw()+ylab("") + xlab("Month")+ labs(title = "")+ theme(legend.position="bottom") +geom_hline(yintercept = 0)  #+theme(axis.text.y=element_blank())#+scale_y_continuous(limits = c(0.05, 0.06))
g3
```


```{r fama_macbeth}

# temp_dh <- delta_hedged[delta_hedged$no_of_days_traded>30 & delta_hedged$time_to_mat_from_last_trd_date<=1, c("secid","investment_date","delta_hedged_return","dh_impl_volatility","dh_bid_ask_t")]
# temp_dh['data_month'] <- as.yearmon(temp_dh$investment_date)
# temp_dh$investment_date <- NULL
# 
# 
# short_fee_dh <- merge(ssf_data,temp_dh,by.x=c("SECID","data_month"),by.y=c("secid","data_month"))
short_fee_dh['year'] <- as.numeric(floor(short_fee_dh$data_month))

months <- unique(short_fee_dh$data_month)
years <- unique(short_fee_dh$year)
library(psych)
trim = 0.005

reg_data <- NULL
for(time in months) {
  tryCatch({
    t <- short_fee_dh[short_fee_dh$data_month==time,]
    if(nrow(t)<20) next
    t<-t[!is.na(t$dh_impl_volatility),]
    reg1 <- lm(log(IndicativeFee)~dh_impl_volatility,data=t)
    t['resid_fee'] <- reg1$residuals
    t['fee_resid_decile'] <- ntile(t$resid_fee,10)

    # reg <- summary(lm(delta_hedged_return~dh_impl_volatility+fee_decile_8,data=t))
    # reg <- summary(lm(delta_hedged_return~dh_impl_volatility+fee_resid_decile,data=t))
    # reg <- summary(lm(delta_hedged_return~dh_impl_volatility+log(IndicativeFee),data=t))
    reg <- summary(lm(delta_hedged_return~dh_impl_volatility+resid_fee,data=t))
    reg_data <- rbind(reg_data,c(time,reg$coefficients[,1][1],reg$coefficients[,1][2],reg$coefficients[,1][3],reg$coefficients[,3][1],reg$coefficients[,3][2],reg$coefficients[,3][3],nrow(t),reg$adj.r.squared))
  },error=function(e){})
}

reg_data <- as.data.frame(reg_data)
mean(reg_data[,2])
mean(reg_data[,2])*sqrt(nrow(reg_data))/sd(reg_data[,2])
mean(reg_data[,3])
mean(reg_data[,3])*sqrt(nrow(reg_data))/sd(reg_data[,3])
mean(reg_data[,4],na.rm=TRUE)
mean(reg_data[,4],na.rm=TRUE)*sqrt(nrow(reg_data))/sd(reg_data[,4],na.rm=TRUE)
# short_fee_dh <- transform(short_fee_dh,date = as.Date(data_month,frac=1))
# short_fee_dh$date <- as.Date(paste(as.numeric(format(short_fee_dh$date,"%Y")),"-",as.numeric(format(short_fee_dh$date,"%m")),"-01",sep=""))
# 
# short_fee_dh <- short_fee_dh[!duplicated(short_fee_dh[c("SECID","date")]),]
# short_fee_dh <- pdata.frame(short_fee_dh,c("SECID","date"))
# 
# fm <- pmg(delta_hedged_return~equity_ret_variance+IndicativeFee,short_fee_dh,index=c("date","SECID"))

```





```{r put_premium_double_sort}
temp <- ssf_data[is.finite(log(ssf_data$put_bid_ask)),]
months <- unique(ssf_data$data_month)
library(psych)
trim = 0.005

sorted_data <- NULL
for(month in months) {
  tryCatch({
    t <- temp[temp$data_month==month,]
    # t['fee_quintile'] <- ntile(t$IndicativeFee,5)
    # t <- t[t$fee_quintile==5,]
    #  t['fee_quintile'] <- ntile(t$IndicativeFee,5)
    #  t <- t[t$fee_quintile==5,]
     t['fee_quintile'] <- ntile(t$IndicativeFee,20)
    t['premium_quintile'] <- 1#ntile(t$put_impl_premium,5)
    t['fee_percentile'] <- t$fee_quintile#paste("Fee",t$fee_quintile,", Prem",t$premium_quintile)
    t <- ddply(t,.(fee_percentile),summarise,
               fee=winsor.mean(IndicativeFee,trim = trim,na.rm=TRUE),
               call_bid_ask=winsor.mean(call_bid_ask,trim = trim,na.rm=TRUE),
               call_option_volume_at_the_money =winsor.mean(call_option_volume_at_the_money/sharesoutstanding,trim = trim,na.rm=TRUE),
               call_premium_to_strike = winsor.mean(call_premium_to_strike,trim = trim,na.rm=TRUE),
               call_open_interest_at_the_money = winsor.mean(call_open_interest_at_the_money/sharesoutstanding,trim = trim,na.rm=TRUE),
               call_impl_volatility = winsor.mean(call_impl_volatility,trim = trim,na.rm=TRUE),
               put_bid_ask=winsor.mean(put_bid_ask,trim = trim,na.rm=TRUE),
               put_option_volume_at_the_money =winsor.mean(put_option_volume_at_the_money/sharesoutstanding,trim = trim,na.rm=TRUE),
               put_premium_to_strike = winsor.mean(put_premium_to_strike,trim = trim,na.rm=TRUE),
               put_open_interest_at_the_money = winsor.mean(put_open_interest_at_the_money/sharesoutstanding,trim = trim,na.rm=TRUE),
               put_impl_volatility = winsor.mean(put_impl_volatility,trim = trim,na.rm=TRUE),
               equity_volume_to_outstanding = winsor.mean(m_sharevolume/sharesoutstanding,trim = trim,na.rm=TRUE),
               market_to_book = winsor.mean(market_value/q_equity,trim = trim,na.rm=TRUE),
               m_equityreturn = winsor.mean(m_equityreturn,trim = trim,na.rm=TRUE),
               equity_ret_variance = winsor.mean(equity_ret_variance,trim = trim,na.rm=TRUE),
               UtilisationByQuantity = winsor.mean(UtilisationByQuantity,trim = trim,na.rm=TRUE),
               no_of_companies = length(unique(SECID))
             )
    t['month'] = month
    sorted_data <- rbind(sorted_data,t)
  },error=function(e){})
}

monthly_data <- sorted_data
monthly_data['year'] <- floor(monthly_data$month)
sorted_data <- ddply(monthly_data,.(fee_percentile),summarise,
                     fee=winsor.mean(fee,trim = trim,na.rm = TRUE),
                     call_bid_ask=winsor.mean(call_bid_ask,trim = trim,na.rm=TRUE),
                     call_option_volume_at_the_money =winsor.mean(call_option_volume_at_the_money,trim = trim,na.rm=TRUE),
                     call_premium_to_strike = winsor.mean(call_premium_to_strike,trim = trim,na.rm=TRUE),
                     call_open_interest_at_the_money = winsor.mean(call_open_interest_at_the_money,trim = trim,na.rm=TRUE),
                     call_impl_volatility = winsor.mean(call_impl_volatility,trim = trim,na.rm=TRUE),
                     put_bid_ask=winsor.mean(put_bid_ask,trim = trim,na.rm=TRUE),
                     put_option_volume_at_the_money =winsor.mean(put_option_volume_at_the_money,trim = trim,na.rm=TRUE),
                     put_premium_to_strike = winsor.mean(put_premium_to_strike,trim = trim,na.rm=TRUE),
                     put_open_interest_at_the_money = winsor.mean(put_open_interest_at_the_money,trim = trim,na.rm=TRUE),
                     put_impl_volatility = winsor.mean(put_impl_volatility,trim = trim,na.rm=TRUE),
                     equity_volume_to_outstanding = winsor.mean(equity_volume_to_outstanding,trim = trim,na.rm=TRUE),
                     market_to_book = winsor.mean(market_to_book,trim = trim,na.rm=TRUE),
                     m_equityreturn = winsor.mean(m_equityreturn,trim = trim,na.rm=TRUE),
                     equity_ret_variance = winsor.mean(equity_ret_variance,trim = trim,na.rm=TRUE),
                     UtilisationByQuantity = winsor.mean(UtilisationByQuantity,trim = trim,na.rm=TRUE),
                     no_of_companies = median(no_of_companies,na.rm=TRUE)
               )

sorted_data_yearly <- ddply(monthly_data,.(fee_percentile,year),summarise,
                     fee=winsor.mean(fee,trim = trim,na.rm = TRUE),
                     call_bid_ask=winsor.mean(call_bid_ask,trim = trim,na.rm=TRUE),
                     call_option_volume_at_the_money =winsor.mean(call_option_volume_at_the_money,trim = trim,na.rm=TRUE),
                     call_premium_to_strike = winsor.mean(call_premium_to_strike,trim = trim,na.rm=TRUE),
                     call_open_interest_at_the_money = winsor.mean(call_open_interest_at_the_money,trim = trim,na.rm=TRUE),
                     call_impl_volatility = winsor.mean(call_impl_volatility,trim = trim,na.rm=TRUE),
                     put_bid_ask=winsor.mean(put_bid_ask,trim = trim,na.rm=TRUE),
                     put_option_volume_at_the_money =winsor.mean(put_option_volume_at_the_money,trim = trim,na.rm=TRUE),
                     put_premium_to_strike = winsor.mean(put_premium_to_strike,trim = trim,na.rm=TRUE),
                     put_open_interest_at_the_money = winsor.mean(put_open_interest_at_the_money,trim = trim,na.rm=TRUE),
                     put_impl_volatility = winsor.mean(put_impl_volatility,trim = trim,na.rm=TRUE),
                     equity_volume_to_outstanding = winsor.mean(equity_volume_to_outstanding,trim = trim,na.rm=TRUE),
                     market_to_book = winsor.mean(market_to_book,trim = trim,na.rm=TRUE),
                     m_equityreturn = winsor.mean(m_equityreturn,trim = trim,na.rm=TRUE),
                     equity_ret_variance = winsor.mean(equity_ret_variance,trim = trim,na.rm=TRUE),
                     UtilisationByQuantity = winsor.mean(UtilisationByQuantity,trim = trim,na.rm=TRUE)
               )


# write.csv(sorted_data,file="sorted_data.csv")
```


```{r call_premium_double_sort}
temp <- ssf_data[is.finite(log(ssf_data$put_impl_premium)),]
months <- unique(ssf_data$data_month)
temp['lendable_frac'] <- temp$LendableQuantity/(temp$sharesoutstanding*1e6)
temp['on_loan_frac'] <- temp$LenderQuantityOnLoan/temp$LendableQuantity
temp['put_vol_open_int'] <- temp$put_opt_volume/temp$put_opt_open_interest
temp['call_vol_open_int'] <- temp$call_opt_volume/temp$call_opt_open_interest

temp$put_vol_open_int <- ifelse(!is.finite(temp$put_vol_open_int),NA,temp$put_vol_open_int)
temp$call_vol_open_int <- ifelse(!is.finite(temp$call_vol_open_int),NA,temp$call_vol_open_int)

sorted_data <- NULL
for(month in months) {
  tryCatch({
    t <- temp[temp$data_month==month,]
    # t['fee_quintile'] <- ntile(t$IndicativeFee,5)
    # t <- t[t$fee_quintile==5,]
    #  t['fee_quintile'] <- ntile(t$IndicativeFee,5)
    #  t <- t[t$fee_quintile==5,]
     t['fee_quintile'] <- ntile(t$IndicativeFee,20)
    t['premium_quintile'] <- 1#ntile(t$put_impl_premium,5)
    t['fee_percentile'] <- t$fee_quintile#paste("Fee",t$fee_quintile,", Prem",t$premium_quintile)
    t <- ddply(t,.(fee_percentile),summarise,fee=mean(IndicativeFee),call_prem=mean(call_impl_premium,na.rm=TRUE),put_prem=mean(put_impl_premium),call_volatility = mean(call_impl_volatility,na.rm=TRUE),put_volatility = mean(put_impl_volatility,na.rm=TRUE),equity_ret_variance=mean(equity_ret_variance,na.rm=TRUE),m_equityreturn=mean(m_equityreturn,na.rm=TRUE),lendable_frac = mean(lendable_frac,na.rm=TRUE),on_loan_frac=mean(on_loan_frac,na.rm=TRUE),put_vol_open_int=mean(put_vol_open_int,na.rm=TRUE),call_vol_open_int=mean(call_vol_open_int,na.rm=TRUE))
    sorted_data <- rbind(sorted_data,t)
  },error=function(e){})
}

sorted_data <- ddply(sorted_data,.(fee_percentile),summarise,fee=mean(fee),call_prem=mean(call_prem),put_prem=mean(put_prem),call_volatility = mean(call_volatility),put_volatility =mean(put_volatility), equity_ret_variance=mean(equity_ret_variance), m_equityreturn=mean(m_equityreturn),lendable_frac = mean(lendable_frac),on_loan_frac=mean(on_loan_frac), put_vol_open_int = mean(put_vol_open_int), call_vol_open_int = mean(call_vol_open_int))

sd = sorted_data

sorted_data$fee <- sorted_data$fee*4
sorted_data$call_volatility <- sorted_data$call_volatility*2
sorted_data$put_volatility <- sorted_data$put_volatility*2
sorted_data$m_equityreturn <- NULL#sorted_data$m_equityreturn*100
sorted_data$equity_ret_variance <- sorted_data$equity_ret_variance*1000
# sorted_data$call_prem <- NULL
# sorted_data$put_prem <- NULL
sorted_data$on_loan_frac <- NULL
sorted_data$lendable_frac <- NULL
sorted_data$call_vol_open_int <- sorted_data$call_vol_open_int/4 
sorted_data$put_vol_open_int <- sorted_data$put_vol_open_int/4

sorted_data <- melt(sorted_data,id="fee_percentile")


g2 <-  ggplot(sorted_data,aes(x=fee_percentile, y=value,colour=variable)) + geom_line(aes(linetype=variable), size=1) +scale_linetype_manual(values = c(1,1,1,1,1,1,1,1))+scale_colour_manual(values=c("black","blue","red","green","darkgreen","purple","coral3","goldenrod"))+ theme_bw()+ylab("") + xlab(" Fee Percentile")+ labs(title = "")+ theme(legend.position="bottom")+  ylim(0,2.5)+theme(axis.text.y=element_blank())#+scale_y_continuous(limits = c(0.05, 0.06))
g2
```

