---
title: "Short Selling Fees and Delta-hedged Returns"
date: "Dec 02, 2017"
output:
  html_document:
    css: bodycss.css
    fig_width: 10
    font-family: Helvetica,Arial,sans-serif;
    number_section: yes
    toc: yes
  pdf_document:
    toc: yes
  word_document:
    toc: yes
linestretch: 2
bibliography: C:\Users\dnratnadiwakara\OneDrive\library.bib
---

<style type="text/css">
body{ 
      font-size: 15px;
      font-family: Helvetica,Arial,sans-serif;
      line-height: 200%;
  }
  
.author {
 font-size: 15px;
 color: Black;
 font-style: normal;
 text-align: center;
}


.date { 
 font-size: 15px;
 color: Black;
 font-style: normal;
 text-align: center;
}

.title{
  text-align: center;
  font-size: 15px;
 color: Black;
 
}

.toc-ignore{
  text-align: center;
  font-size: 15px;
 color: Black;
}

.fluid-row{
  text-align: center;
  font-size: 15px;
 color: Black;
}

</style>

```{r setup, include=FALSE}
knitr::opts_chunk$set(warning=FALSE, message=FALSE,echo = FALSE, fig.align='center')
```



```{r initialize,message=FALSE,warning=FALSE}
rm(list=ls())
path = "E:/shortselling"
setwd(path)
require(gdata)
require(dplyr)
require(zoo)
require(plyr)
require(sqldf)
require(stargazer)
require(data.table)
require(lubridate)
require(lfe)
library(np)
library(ggplot2)
library(psych)


trim = 0.005

output.type="text"

ssf_data <- readRDS(file="E:/shortselling/Data/Processed/Monthly_sample_Nov122017.rds")
ssf_data <- as.data.frame(ssf_data)
ssf_data['data_date'] <- as.Date(ssf_data$data_month)





delta_hedged <- read.csv(file="E:/shortselling/Data/Processed/delta_hedged_returns_Nov202017.csv",sep="|",header = FALSE)
names(delta_hedged) <- c("secid","optionid","investment_date","maturity_date","strike_price","c_t","s_t","s_t_T","term1","term2","term2_alt","payoff","investment","no_of_days_traded","dh_bid_ask_t","dh_option_volume_mean","dh_open_interest_mean","last_traded_date","c_t_T","dh_impl_volatility","delta")

 # record <- c(call[1,]$secid,optionid,investment_date,maturity_date,call[nrow(call),]$strike_price,call[1,]$c_t,call[1,]$underlying_price,call[nrow(call),]$underlying_price,term1,term2,term2_alt,payoff,investment,nrow(call),call[1,]$bid_ask,mean(call$option_volume,na.rm = TRUE),mean(call$open_interest,na.rm = TRUE),call[nrow(call),]$date,call[nrow(call),]$c_t,call[1,]$impl_volatility,call[(nrow(call)-1),]$delta)
 
delta_hedged$investment_date <- as.Date(delta_hedged$investment_date)
delta_hedged$maturity_date <- as.Date(delta_hedged$maturity_date)
delta_hedged$last_traded_date <- as.Date(delta_hedged$last_traded_date)

delta_hedged['delta_hedged_return'] <- (delta_hedged$payoff - delta_hedged$term1 - delta_hedged$term2)/delta_hedged$investment
delta_hedged['time_to_maturity'] <- as.numeric(delta_hedged$maturity_date -delta_hedged$investment_date)
delta_hedged['time_to_mat_from_last_trd_date'] <- as.numeric(delta_hedged$maturity_date-delta_hedged$last_traded_date)
delta_hedged['moneyness'] <- delta_hedged$s_t/delta_hedged$strike_price




  # permcos <- unique(ssf_data$PERMCO)
  # permcos <- permcos[!is.na(permcos)]
  # permcos <- paste("",permcos,"",collapse=", ",sep="")
  # run_query(paste("select DATE,PERMCO,DIVAMT  from CRSPA.DSE where DISTCD<=1999 and DISTCD>=1000 and year(DATE)>=2002 and PERMCO in (",permcos,") and DIVAMT>0",sep=""))
  # fetch_last_query(name="dividend",rows = -1)
  # dividend$DATE <- as.Date(dividend$DATE)
  # saveRDS(dividend, file="E:/shortselling/Data/Processed/dividend.rds")

dividend <- readRDS(file="E:/shortselling/Data/Processed/dividend.rds")

temp_dh <- delta_hedged[delta_hedged$no_of_days_traded>30 & delta_hedged$time_to_mat_from_last_trd_date<=1, c("secid","investment_date","delta_hedged_return","dh_impl_volatility","c_t","strike_price","dh_bid_ask_t","maturity_date","time_to_mat_from_last_trd_date","no_of_days_traded","moneyness","time_to_maturity","s_t","c_t")]
temp_dh['data_month'] <- as.yearmon(temp_dh$investment_date)

short_fee_dh <- merge(ssf_data,temp_dh,by.x=c("SECID","data_month"),by.y=c("secid","data_month"))

short_fee_dh['month1'] <- as.yearmon(short_fee_dh$investment_date)
short_fee_dh['month2'] <- as.yearmon(short_fee_dh$investment_date+28)
short_fee_dh['month3'] <- as.yearmon(short_fee_dh$maturity_date)
dividend['month1'] <- as.yearmon(dividend$DATE)
dividend <- dividend[!duplicated(dividend[c("month1","PERMCO")]),]
short_fee_dh <- merge(short_fee_dh,dividend[,c("month1","PERMCO","DATE")],by=c("month1","PERMCO"),all.x = TRUE)
dividend$month1 <- NULL
dividend['month2'] <- as.yearmon(dividend$DATE)
short_fee_dh <- merge(short_fee_dh,dividend[,c("month2","PERMCO","DATE")],by=c("month2","PERMCO"),all.x = TRUE)
dividend['month3'] <- as.yearmon(dividend$DATE)
names(dividend) <- c( "DATE.z","PERMCO","DIVAMT","month2","month3")
dividend$month2 <- NULL
short_fee_dh <- merge(short_fee_dh,dividend[,c("month3","PERMCO","DATE.z")],by=c("month3","PERMCO"),all.x = TRUE)

short_fee_dh <- as.data.frame(short_fee_dh)
short_fee_dh['div_date'] <- short_fee_dh$DATE.y
short_fee_dh$div_date <- ifelse(is.na(short_fee_dh$div_date),short_fee_dh$DATE.z,short_fee_dh$div_date)
short_fee_dh$div_date <- ifelse(is.na(short_fee_dh$div_date),short_fee_dh$DATE.x,short_fee_dh$div_date)
short_fee_dh$DATE.x <- NULL
short_fee_dh$DATE.y <- NULL
short_fee_dh$DATE.z <- NULL

short_fee_dh <- short_fee_dh[is.na(short_fee_dh$div_date) | (short_fee_dh$div_date<= short_fee_dh$investment_date | short_fee_dh$div_date>= short_fee_dh$maturity_date),]
short_fee_dh <- short_fee_dh[short_fee_dh$s_t >= short_fee_dh$c_t,]

short_fee_dh <- short_fee_dh[short_fee_dh$no_of_days_traded>30 & short_fee_dh$time_to_mat_from_last_trd_date<=1,]

```


# Descriptives
```{r descriptives}
stargazer(short_fee_dh[, c("delta_hedged_return","time_to_maturity","moneyness","IndicativeFee")], type = output.type, summary.stat = c("mean", "sd", "p25", "median", "p75", "n"),notes = "",digits = 4)

```



# Returns of delta-hedged calls: portfolio sorts by stock volatility
```{r sorted_by_vol}

months <- unique(short_fee_dh$data_month)

sorted_data <- NULL
for(month in months) {
  tryCatch({
    t <- short_fee_dh[short_fee_dh$data_month==month,]
    if(nrow(t)<20) next
    reg1 <- lm(log(IndicativeFee)~dh_impl_volatility,data=t)
    t['resid_fee'] <- reg1$residuals
    t['fee_pf'] <- 1#ntile(t$resid_fee,10)
    t['vol_pf'] <- ntile(t$dh_impl_volatility,10)
   
    t['premium_to_strike']<-t$c_t/t$strike_price

    t <- ddply(t,.(fee_pf,vol_pf),summarise,
               delta_hedged_return=winsor.mean(delta_hedged_return,trim=trim,na.rm=TRUE)
             )
    t['month'] = month
    sorted_data <- rbind(sorted_data,t)
  },error=function(e){})
}

vol_sorted_data <- ddply(sorted_data,.(fee_pf,vol_pf),summarise,
                     delta_hedged_return = winsor.mean(delta_hedged_return,trim=trim,na.rm = TRUE)
               )

g1 <- ggplot(data=vol_sorted_data, aes(x=vol_pf, y=delta_hedged_return)) +
    geom_bar(stat="identity")
g1

```


# Returns of delta-hedged calls: portfolio sorts by residual of log(short fee) on implied volatility
```{r sorted_by_fee_resid}

sorted_data <- NULL
for(month in months) {
  tryCatch({
    t <- short_fee_dh[short_fee_dh$data_month==month,]
    if(nrow(t)<20) next
    reg1 <- lm(log(IndicativeFee)~dh_impl_volatility,data=t)
    
    t['resid_fee'] <- reg1$residuals
    t['fee_pf'] <- ntile(t$resid_fee,10)
    t['vol_pf'] <- 1#ntile(t$dh_impl_volatility,10)
   
    t['premium_to_strike']<-t$c_t/t$strike_price

    t <- ddply(t,.(fee_pf,vol_pf),summarise,
                         delta_hedged_return=winsor.mean(delta_hedged_return,trim=trim,na.rm=TRUE)
             )
    t['month'] = month
    sorted_data <- rbind(sorted_data,t)
  },error=function(e){})
}

monthly_data <- sorted_data
monthly_data['year'] <- floor(monthly_data$month)
sorted_data <- ddply(monthly_data,.(fee_pf,vol_pf),summarise,
                     delta_hedged_return = winsor.mean(delta_hedged_return,trim=trim,na.rm = TRUE)
               )
g2 <- ggplot(data=sorted_data, aes(x=fee_pf, y=delta_hedged_return)) +
    geom_bar(stat="identity")
g2
```

# Time series of returns of residual of short fee based option trading strategy
```{r time_series_returns}

im_vol <- monthly_data[monthly_data$fee_pf %in% c(1,8,10),c("fee_pf","delta_hedged_return","month")]


months <- unique(im_vol$month)

im_vol_summary <- NULL
for(month in months) {
  temp <- im_vol[im_vol$month==month,]
  im_vol_summary <- rbind(im_vol_summary,c(month,temp[temp$fee_pf==1,]$delta_hedged_return,temp[temp$fee_pf==8,]$delta_hedged_return,temp[temp$fee_pf==10,]$delta_hedged_return))
}
im_vol_summary <- as.data.frame(im_vol_summary)
names(im_vol_summary) <- c("month","d1","d8","d10")
im_vol_summary['d8_d1'] <- im_vol_summary$d8-im_vol_summary$d1
# im_vol_summary['d10_d8'] <- im_vol_summary$d10-im_vol_summary$d8
im_vol_summary['d10_d1'] <- im_vol_summary$d10 - im_vol_summary$d1

im_vol_summary$d1 <- NULL
im_vol_summary$d8 <- NULL
im_vol_summary$d10 <- NULL

im_vol_summary <- melt(im_vol_summary,id="month")
im_vol_summary$variable <- as.character(im_vol_summary$variable)

g3 <-  ggplot(im_vol_summary,aes(x=month, y=value,colour=variable)) + geom_line(aes(linetype=variable), size=1) +scale_linetype_manual(values = c(1,1))+scale_colour_manual(values=c("blue","red"))+ theme_bw()+ylab("50 day return") + xlab("Month")+ labs(title = "")+ theme(legend.position="bottom") +geom_hline(yintercept = 0)+geom_hline(aes(yintercept=mean(im_vol_summary[im_vol_summary$variable=="d8_d1",]$value)), color="red", linetype="dashed")+geom_hline(aes(yintercept=mean(im_vol_summary[im_vol_summary$variable=="d10_d1",]$value)), color="blue", linetype="dashed")
g3
```

# Fama-MacBeth Regression: Delta-hedged return ~ impl. volatility + short fee residual

```{r fama_macbeth_1}

months <- unique(short_fee_dh$data_month)


reg_data <- NULL
for(time in months) {
  tryCatch({
    t <- short_fee_dh[short_fee_dh$data_month==time,]
    if(nrow(t)<20) next
    t<-t[!is.na(t$dh_impl_volatility),]
    reg1 <- lm(log(IndicativeFee)~dh_impl_volatility,data=t)
    t['resid_fee'] <- reg1$residuals
    reg <- summary(lm(delta_hedged_return~dh_impl_volatility+resid_fee,data=t))
    reg_data <- rbind(reg_data,c(time,reg$coefficients[,1][1],reg$coefficients[,1][2],reg$coefficients[,1][3],reg$coefficients[,3][1],reg$coefficients[,3][2],reg$coefficients[,3][3],nrow(t),reg$adj.r.squared))
  },error=function(e){})
}

reg_data <- as.data.frame(reg_data)

print(paste("Intercept: ",round(mean(reg_data[,2]),4),"(t=",round(mean(reg_data[,2])*sqrt(nrow(reg_data))/sd(reg_data[,2]),2),")"))
print(paste("Imp. Volatility: ",round(mean(reg_data[,3]),4),"(t=",round(mean(reg_data[,3])*sqrt(nrow(reg_data))/sd(reg_data[,3]),2),")"))
print(paste("Short fee resid : ",round(mean(reg_data[,4]),4),"(t=",round(mean(reg_data[,4])*sqrt(nrow(reg_data))/sd(reg_data[,4]),2),")"))
print(paste("Adj. R2: ",round(mean(reg_data[,9]),4)))


t <- reg_data[,c(1,4)]
names(t) <- c("month","coef_of_fee_resid")
g4 <- ggplot(t, aes(x = month, y = coef_of_fee_resid)) + geom_line() +geom_hline(yintercept = 0)
g4

```


# Fama-MacBeth Regression: Delta-hedged return ~ impl. volatility + log(short fees)

```{r fama_macbeth_2}

months <- unique(short_fee_dh$data_month)


reg_data <- NULL
for(time in months) {
  tryCatch({
    t <- short_fee_dh[short_fee_dh$data_month==time,]
    if(nrow(t)<20) next
    t<-t[!is.na(t$dh_impl_volatility),]
    reg1 <- lm(log(IndicativeFee)~dh_impl_volatility,data=t)
    t['resid_fee'] <- reg1$residuals
    reg <- summary(lm(delta_hedged_return~dh_impl_volatility+log(IndicativeFee),data=t))
    reg_data <- rbind(reg_data,c(time,reg$coefficients[,1][1],reg$coefficients[,1][2],reg$coefficients[,1][3],reg$coefficients[,3][1],reg$coefficients[,3][2],reg$coefficients[,3][3],nrow(t),reg$adj.r.squared))
  },error=function(e){})
}

reg_data <- as.data.frame(reg_data)

print(paste("Intercept: ",round(mean(reg_data[,2]),4),"(t=",round(mean(reg_data[,2])*sqrt(nrow(reg_data))/sd(reg_data[,2]),2),")"))
print(paste("Imp. Volatility: ",round(mean(reg_data[,3]),4),"(t=",round(mean(reg_data[,3])*sqrt(nrow(reg_data))/sd(reg_data[,3]),2),")"))
print(paste("log(short fees): ",round(mean(reg_data[,4]),4),"(t=",round(mean(reg_data[,4])*sqrt(nrow(reg_data))/sd(reg_data[,4]),2),")"))
print(paste("Adj. R2: ",round(mean(reg_data[,9]),4)))


t <- reg_data[,c(1,4)]
names(t) <- c("month","coef_of_log_short_fees")
g4 <- ggplot(t, aes(x = month, y = coef_of_log_short_fees)) + geom_line() +geom_hline(yintercept = 0)
g4

```

